ManyPrimates-2021

### 2024-10-22 doc/charting/ManyPrimates-2021.qmd
added a few points to this paper

-   Github - version control - all
-   Registered reports - help designing analysis to prove specific hypothesis - study design
-   p-curve software - helps avoiding overrepresantation of positive results - 
-   A.P.E.S Wiki - open access platform for standardized research and conservation of the data - they report it as an outcome of large-scale collaboration
-   PRIMatE Research Exchange - platform to exchange data, ideas and protocols - they report it as an outcome of large-scale collaboration

@@

-   They developed ethical guidelines for all collaborators (non-invasive research, always open science, author list)
-   They ran a pilot study that tried replicating analysis on short-term memory with more sample size.
-   They preregistered protocols, created code and hosted data in repositories so that other coworkers can run the analysis systematically.
-   Data was collected.
-   Other workforce merged the data and visualized the results.
-   With this pipeline, they decided to run other analysis. This highlights the importance of a good test study.

>>>>

-   Github - version control - all
-   Registered reports - help designing analysis to prove specific
    hypothesis - planning
-   p-curve software - helps avoiding overrepresantation of positive
    results - analysis
-   A.P.E.S Wiki - open access platform for standardized research and
    conservation of the data - dissemination
-   PRIMatE Research Exchange - platform to exchange data, ideas and
    protocols - dissemination

@@

-   They developed ethical guidelines for all collaborators
    (non-invasive research, always open science, author list)
-   Research questions are selected democratically - proposals for
    projects are submitted and members vote to select which projects
    will be carried out
-   They ran a pilot study that tried replicating analysis on short-term
    memory with more sample size.
-   They preregistered protocols, created code and hosted data in
    repositories so that other coworkers can run the analysis
    systematically.
-   Data was collected.
-   Other workforce merged the data and visualized the results.
-   With this pipeline, they decided to run other analysis. This
    highlights the importance of a good test study.
-   Task forces within the project prepared different materials they
    then uploaded to github and pre-register
